### 2013-12-30 conclusions.tex
corrected variable error

\section{Conclusions}
The delineation of prostate zonal anatomy in ARFI images has been compared with
the established methods for identifying zonal anatomy using MR T2W images.
Both imaging modalities showed moderate correlations between estimated organ
volume and gross pathologic weights, and ARFI:MR total prostate gland volumes
were well-correlated (R$^2$ = \MRarfiVolTotalRsq), but ARFI images yielded
prostate volumes that were, on average, larger (\MRarfiVolTotalMeanDiff\%~$\pm$
\MRarfiVolTotalStdDiff\%) than MR images, primarily due to over-estimation of
the lateral dimension of the prostate total gland (\ARFImrTotalLatLatMeanPct~
$\pm$ \ARFImrTotalLatLatStdPct\%), while differences in the other dimensions
were less significant contributors (\ARFImrTotalAntPostMeanPct~$\pm$
\ARFImrTotalAntPostStdPct\%~and \ARFImrTotalApexBaseMeanPct~$\pm$
\ARFImrTotalApexBaseStdPct\%).  The central zone volumes of ARFI and MR images
were also well-correlated (R$^2$ = \MRarfiVolCentralRsq), with minimal volume
bias between the imaging modalities, but significant variability case-to-case
(\MRarfiVolCentralMeanDiff~$\pm$ MRarfiVolCentralStdDiff\%).  Central zone
volume differences were, again, strongly attributed to over-estimation of the
lateral dimension (\ARFImrCentralLatLatMeanPct~$\pm$
\ARFImrCentralLatLatStdPct\%), with a significant underestimation of the
apex-to-base dimension (\ARFImrCentralAntPostMeanPct~$\pm$
\ARFImrCentralAntPostStdPct\%).  Strong variability in CG volumes is believed
to be related to the extent of BPH for select cases.  Overall, ARFI imaging of
the prostate yielded prostate volumes and dimensions that were correlated with
MR T2WI estimates, with differences in the lateral and apex-to-base dimensions.
Poor image contrast between the prostate and peri-prostatic fat may be one
cause of these differences.  ARFI imaging is a promising low-cost, real-time
imaging modality that can compliment MR imaging for diagnosis, treatment
planning and management of PCa.

>>>>

\section{Conclusions}
The delineation of prostate zonal anatomy in ARFI images has been compared with
the established methods for identifying zonal anatomy using MR T2W images.
Both imaging modalities showed moderate correlations between estimated organ
volume and gross pathologic weights, and ARFI:MR total prostate gland volumes
were well-correlated (R$^2$ = \MRarfiVolTotalRsq), but ARFI images yielded
prostate volumes that were, on average, larger (\MRarfiVolTotalMeanDiff\%~$\pm$
\MRarfiVolTotalStdDiff\%) than MR images, primarily due to over-estimation of
the lateral dimension of the prostate total gland (\ARFImrTotalLatLatMeanPct~
$\pm$ \ARFImrTotalLatLatStdPct\%), while differences in the other dimensions
were less significant contributors (\ARFImrTotalAntPostMeanPct~$\pm$
\ARFImrTotalAntPostStdPct\%~and \ARFImrTotalApexBaseMeanPct~$\pm$
\ARFImrTotalApexBaseStdPct\%).  The central zone volumes of ARFI and MR images
were also well-correlated (R$^2$ = \MRarfiVolCentralRsq), with minimal volume
bias between the imaging modalities, but significant variability case-to-case
(\MRarfiVolCentralMeanDiff~$\pm$ \MRarfiVolCentralStdDiff\%).  Central zone
volume differences were, again, strongly attributed to over-estimation of the
lateral dimension (\ARFImrCentralLatLatMeanPct~$\pm$
\ARFImrCentralLatLatStdPct\%), with a significant underestimation of the
apex-to-base dimension (\ARFImrCentralAntPostMeanPct~$\pm$
\ARFImrCentralAntPostStdPct\%).  Strong variability in CG volumes is believed
to be related to the extent of BPH for select cases.  Overall, ARFI imaging of
the prostate yielded prostate volumes and dimensions that were correlated with
MR T2WI estimates, with differences in the lateral and apex-to-base dimensions.
Poor image contrast between the prostate and peri-prostatic fat may be one
cause of these differences.  ARFI imaging is a promising low-cost, real-time
imaging modality that can compliment MR imaging for diagnosis, treatment
planning and management of PCa.
